A quantitative framework for investigating the reliability of empirical network construction

### 2019-03-05 manuscript/reply_to_reviewers_2.tex

			I think the authors miss one key discomfort with empirical Bayes. It seems vaguely anti-ecology, because it assumes that we can L289 : “use information from abundant and easily-sampled species to predict interaction probabilities for species which were observed only rarely.”  A common goal in network ecology is to describe interaction frequencies by using niche-based proxies (phylogeny, traits, etc). If it was a simply a matter that most networks had the same degree distribution, then predicting networks would be much easier than it is. In fact, we are really bad at predicting pairwise interactions (see Olito and Fox), even when we get the emergent structure of the network correct. Yet empirical Bayes assumes a kind of commonality among all networks to help narrow the posteriors. I think the authors need to speak to this concern.

		\end{refquote}

		\textbf{R:} We appreciate but do not fully share the Reviewer's negative view of empirical Bayes. Perhaps this is a matter of perspective: in a system where a great deal of information about the traits structuring interactions is known and trait values are available for most species, trait-based models are indeed often a good way to predict interactions (although far from fool-proof, as the Reviewer points out). This is why we began our section on informative priors with trait-based models and only introduce empirical and approximate Bayes as solutions where trait information/models are lacking or where over-fitting is a strong concern. Most of the authors of this manuscript are more used to such relatively information-poor systems. In these cases, we agree that empirical Bayes is not perfect, but argue that it is much better than nothing (or an uninformative prior, as long as a somewhat similar network is available).

		% [[Currently one vote for removing this paragraph and one vote for keeping it and strengthening the point]]
		An uninformative prior like the Jeffreys prior gives a maximum likelihood estimate of 0.5 for the probability of an interaction between two species which have never been observed together. Based on our understanding of ecological systems, this seems highly unlikely. Certainly species differ in many ways, but they also do have some similarities, such as limited foraging time and somewhat consistent morphologies. Because of behavioural, morphological, or temporal limits to the number of partners with which a given species can interact, most ecological networks are sparse and most well-sampled species interact with only a small subset of their potential partners (extreme generalists in highly nested mutualistic networks being a notable exception). We can therefore reasonably expect that a species entering a new habitat, for example, will interact with far fewer than half of the available partners. If we do not know which traits strongly affect interactions involving the focal species, or if those traits are not known for all of the species in the network, we cannot use a trait-based model to predict interaction frequencies. This leaves empirical and approximate Bayes as the only viable options, unless we are willing to revert to the assumption that unobserved interactions never occur. Certainly empirical Bayes is not perfect, but we are confident that it is still gives more reasonable expectations than ignoring the ecological networks literature completely.

		Moreover, while we agree that empirical Bayes does not take differences in niche proxies into account, this may not be crucial in all studies. Researchers are often more interested in the overall structure of the network or in some emergent property such as stability than in the relationships between niche proxies and interaction frequencies. In such cases, the number of additional interactions that we expect to be observed with further sampling can be more important than the exact identity of those interactions, and an empirical Bayes approach is reasonable if a good trait-based model and trait information or not available.

		Finally, we disagree with the Reviewer's contention that ``empirical Bayes assumes a kind of commonality among all networks". This is not so; empirical Bayes only assumes some commonality between the focal network and \emph{those used to construct the prior}. Empirical Bayes does not imply anything about networks not referred to in the prior. We have revised the text to emphasise the need to use similar networks to construct an empirical Bayes prior and note that \emph{Appendix S7} demonstrates the pitfalls of basing an empirical Bayes prior on a network with little commonality with the focal system.

		We believe that including an expanded reference to \emph{Appendix S7} as suggested below will help to address some of these concerns by demonstrating that empirical Bayes should \emph{not} be based on networks which have major differences from the focal system as this will lead to unreasonable predictions (in our case, although the taxa and interaction types involved were similar, the taxonomic resolutions in \citet{Barbour2016} and \citet{Kopelke2017} were very different). To reinforce this point and make the role of empirical Bayes as a solution in the absence of trait-based models and/or trait information, we have made several minor revisions to the section introducing informative priors. We hope that these changes will be sufficient to illustrate the drawbacks to empirical Bayes without being overly discouraging for those who lack the necessary information to construct more detailed informative priors.

### 2019-03-05 manuscript/coverletter_revision_2.tex
resubmitted second round March 5

    My co-authors and I are pleased to resubmit our manuscript 
    MEE-18-07-452:  \emph{A quantitative framework for investigating the reliability of empirical network construction} for consideration as a research article in \textbf{Methods in Ecology and Evolution}. Dr. Aaron Ellison, Senior Editor, noted that the Associate Editor and four reviewers ``\emph{recognise a kernel of important work in this manuscript}" but that a significant shift in emphasis was necessary for this kernel to shine through. We believe that this revision has addressed the Associate Editor's and Reviewers' concerns and that our manuscript is clearer and more polished as a result. We thank them for their careful feedback.

@@

    We appreciate the opportunity to resubmit our manuscript and thank you for your continued consideration. We remain confident that our manuscript will be of broad interest to the readers of \textbf{Methods in Ecology and Evolution} because of the general nature of uncertainty around interactions and the broadly-applicable solution we offer. We are confident that our worked example and easy-to-use scripts will provide a useful template for empiricists and theoreticians alike. We hope that you agree and eagerly await your reply.

>>>>

    My co-authors and I are pleased to resubmit a second revision of our manuscript  MEE-18-07-452:  \emph{A quantitative framework for investigating the reliability of empirical network construction} for consideration as a research article in \textbf{Methods in Ecology and Evolution}. Dr. Aaron Ellison, Senior Editor, noted that the reviewer who provided additional feedback was very positive about our revision but requested more discussion about prior choice. We have expanded our discussion to emphasise the need for careful prior selection and now refer to a demonstration of problems that can result from a poorly-chosen prior. We believe that these additions, although slightly exceeding the normal length restrictions of \textbf{Methods in Ecology and Evolution}, have improved the manuscript enough to justify the extra length. We thank the Editor for his encouragement and the Reviewer for his further thoughtful feedback.

@@

    We appreciate the opportunity to resubmit a further revision of our manuscript and thank you for your continued consideration. We remain confident that our manuscript will be of broad interest to the readers of \textbf{Methods in Ecology and Evolution}. We hope that you agree and eagerly await your reply.
